MinCall --- MinION end2end deep learning basecaller

### 2017-06-30 paper/main.tex
Moved to appendix

Earlier models were Hidden Markov model(HMM)-based where hidden state modeled DNA sequence of length 6 (6-mer) in the nanopore. Pore models were used in computing emission probabilities.~\cite{loman2015complete,schreiber2015analysis,szalay2015novo,timp2012dna} and the recent open source HMM-based basecaller Nanocall~\cite{david2016nanocall}.

\textit{DeepNano}~\cite{deepnano} is open source RNN basecalled whose model are trained with older R7 chemisty, and thus are excluded from later analysis, yet it's mentioned here for completeness (or attempt thereof).

@@

% set style - not sure which one is official for papers
% spbasic (springer basic makes sense)
\bibliographystyle{spbasic}
\bibliography{refs}
\end{document}

>>>>

Earlier models were Hidden Markov model(HMM)-based where hidden state modeled DNA sequence of length 6 (6-mer) in the nanopore. Pore models were used in computing emission probabilities.~\cite{loman2015complete,schreiber2015analysis,szalay2015novo,timp2012dna} and the recent open source HMM-based basecaller Nanocall~\cite{david2016nanocall}. Modern basecallers use RNN base models, and we opted out using CNN instead with beam search.

We compared our model on R9 chemistry with Metrichorn (HMM based approach) and Albacore (RNN based approach). For detailed basecaller overview  see the appendix~\ref{app:basecallers}.

@@

% set style - not sure which one is official for papers
% spbasic (springer basic makes sense)
\bibliographystyle{spbasic}
\bibliography{refs}
\appendix
\section{Basecallers}\label{app:basecallers}

\textit{Nanocall} \cite{David046086} was the first third-party open source basecaller for nanopore data. It uses HMM approach like the original R7 Metrichor. Nanocall does not support newer chemistries after R7.3.

\textit{DeepNano} \cite{Boza2017}  was the first open-source basecaller based on neural networks. It uses bidirectional recurrent neural networks implemented in Python, using the Theano library. When released, originally only supported R7 chemistry, but support for R9 and R9.4 was added recently.

\end{document}
